{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-07 Paper/main.tex
Small changes

	\section{Theory}\label{Theory}
	{\color{red} Introductory Sentence Here!} In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$. However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space. Therefore, it is necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects. One integral concept in inferential statistics is random variables. Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.
	A typical case is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers. As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space. A formalization of this idea makes some more theoretical considerations necessary. The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015}.

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	As mentioned above, the realized curves can be expressed in terms of a chosen functional basis. For this expansion, it is technically possible to use a complete basis of $\mathbb{L}^2[0,1]$. In many cases this is not a desirable approach as the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis. {\color{red} Therefore, methods such as acceleration penalties have to be employed to smooth the function.} On the other hand, important information on the curves could be missed by using a number of basis functions that is too small. In that sense, this discussion is subject to the Bias-Variance tradeoff. It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves. The basis expansion with truncation is defined by
	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or other criteria. The influence of this truncation on the prediction accuracy of different estimates is the subject of the simulation study. {\color{red} Add text for figure}

>>>>

	\section{Theory}\label{Theory}
	To allow for scalar-on-function regression, it is necessary to extend some concepts from multivariate regression to the realm of infinite-dimensional objects, as the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space. One integral concept that has to be defined is a random function as a special case of a random variable. Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space. 
	The typical case for a random variable realizing i $\mathbb{R}$ is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers. As a first intuition for the concept of a random function, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space. A formalization of this idea makes some more in-depth considerations necessary. The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015} and chapters 4.4 and 4.6 from \cite{kokoszka_introduction_2017}.

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	As mentioned above, the realized curves can be expressed in terms of a chosen functional basis. For this expansion, it is technically possible to use a complete basis of $\mathbb{L}^2[0,1]$. In many cases this is not a desirable approach as the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis. {\color{red} Therefore, methods such as acceleration penalties have to be employed to smooth the function.} On the other hand, important information on the curves could be missed by using a number of basis functions that is too small. In that sense, this discussion is subject to the Bias-Variance tradeoff. It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves. The basis expansion with truncation is given by Equation \ref{basis_exp}.

	\begin{equation}\label{basis_exp}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}

	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method such as Cross-Validation. The influence of this truncation on the prediction accuracy of different estimates is the subject of the simulation study. {\color{red} Add text for figure}
